Visualizations for the manuscript

### 2022-03-16 metanalysis_visualization/manuscript_Figures.Rmd
fixing bootstrap

bootstrapped <- count_icd_all %>% 
  group_by(siteid) %>% 
  group_map( ~bootstrapping_slopes(.x, bootstrap_size = bootstrap_size))
names(test) <- unique(count_icd_all$siteid)

@@

### R session information

```{r, results='hide'}
sessionInfo()

>>>>

bootstrapped <- count_icd_all_boot %>% 
  group_by(siteid) %>% 
  group_map( ~bootstrapping_slopes(.x, bootstrap_size = bootstrap_size))
names(bootstrapped) <- unique(count_icd_all$siteid)

@@
